How to compute the fusion product of MV cycles in type $A$

### 2021-05-27 draft.tex
up to 63

\subsection{The fusion construction}
\jcom{We should probably be consistent with $ \AA$ vs $\CC$.  I'm happy with either.}
\acom{Do you mean that if we go with $\AA$ we should change $\AA^\times$ as well? Also, would you agree that the distinction is the topology? So $\AA$ is better if we were using ``generic'' to describe $s\ne 0$, which we are not.}
\jcom{Yes, either we should write $ \AA, \AA^\times $ or $ \CC, \AA^\times$.  There is no distinction.  Always in this paper, we work with the Zariski topology whether we write $ \AA $ or $ \CC$.}
\acom{Ok, let's be fancy and write $\AA$. (So if someone writes $s\to 0$ you don't think of it as $s$ approaches $0$ in the metric topology, but really as the limit of ideals $(s)\supset (s^2)\supset \cdots$ which, I hope, is the zero ideal?)}

@@

For $ s \in \CC$ we write $ J_{s,\lambda}$ for the Jordan form matrix with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$.

\begin{definition}
\label{def:Olam}
The nilpotent orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.
\end{definition}  
% 
% Temporarily commenting out, don't use
% Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
% 
\begin{definition}
\label{def:Olamlam}
    For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
\end{definition}  
% 
These matrices and the linear operators they represent will be said to have Jordan type $((0,\lambda'), (s,\lambda''))$.

@@

We recall that these adjoint orbit closures are given by rank conditions.  
More precisely we have
$$
    \overline{\OO}^\lambda = \{ A \in M_N(\CC) : \rk A^i \le N - \#\text{~boxes in first $i$ columns of }\lambda \}
$$
and
\begin{equation} 
\label{eq:ranks}
\begin{split}
    % 
    \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : \rk A^i &\le N - 
    \#\text{~boxes in first $i$ columns of }\lambda' \\
    \rk (A-s)^i &\le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}\,. 
\end{split}
\end{equation}
%

@@

Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ (called a rank function).  Let $k $ be maximal such that $ r(k) \ne 0 $.
% \jcom{I don't know if it is really necessary to introduce this $ k$.  Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.} \acom{And make it $N$? Was $k = m$ replaced because $m$ is already used?} \jcom{Yes and yes} \acom{I like the idea of making it $N$}

Let $ W$ be a subspace of $ \AA^k$. Eisenbud \& Saltman define a flat family $ X_{r,W} \rightarrow W$, whose fibres are reduced and defined by rank conditions. We will now describe these fibres.

Let $ z \in \AA^k$. Some of the coordinates of $z$ may be equal; we introduce some data to keep track of these equalities. There exist $ 0=k_0< k_1< \dots < k_\ell = k $, distinct $ s_1, \dots, s_\ell \in \CC$ and a permutation  $ p $ of $ \{1, \dots, k\}$ such that 
$$ s_j = z_{p(k_{j-1}+1)} = \cdots = z_{p(k_j)}\,. $$ We require that $ p $ is of minimal length, given the choice of $ s_1, \dots, s_\ell$.  The data $s_\bullet, p, k_\bullet$ is unique up to a permutation of $ \{1, \dots, \ell\}$.
% 
%\jcom{Eisenbud--Saltman don't introduce this $ s_j$ notation, but I find it helpful.}
% 
%\acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}
%\jcom{That is what I was trying to say with ``introduce some data \dots''  Maybe it could be more clear.  I also clarified the uniqueness.}
%\acom{Oh, sorry, I see it. Maybe because it was the start of a new paragraph I didn't connect `data' and `ranks' at first glance.}

Next for $ j = 1, \dots \ell $ and $ i = 1, \dots, k_{j+1} - k_j$, we define
$$
    % r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
    r_{z,j}(i):= N + \sum_{a = 1}^i r(p(k_j + a)) - r(p(k_j +a) - 1)  \, . 
$$
\jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
%\jcom{I fixed it now.  I didn't want to use ES's $a_i$.} 
%\acom{\emoji{+1}}

@@

For $ s \in \CC$, we define $ z(s) \in \CC^k$, with $ z(s)_{p(j)} = 0 $ for $ j = 1, \dots, k_1 $ and $ z(s)_{p(j)} = s $ for $ j = k_1 + 1, \dots, k$.

For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of $ \ell = 2$, $k_1$, $s_1 = 0$, $s_2 = s$, and the permutation $p $.
We also see that
\begin{equation} 
\label{eq:rcols}
    \begin{split}
            r_{z(s), 1}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda' \\
            r_{z(s), 2}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda'' \,. 
    \end{split}
\end{equation}
On the other hand, for $z(0)$, we get that $ r = 1$ and that 
\begin{equation} 
\label{eq:rcol2}
    r_{z(0),1}(i) = 
    r(i) = N - \#\text{~boxes in first $i$ columns of }\lambda\,. 
\end{equation}
%\jcom{Someone should check that I chose the notation correctly to make this work out.}
% 
%\acom{What do we mean by equalities in $z(s)$ reproduce $p$? I thought $z(s)$ was defined by $p$. Also, $r_{z(s),1}(i) = N- r(p(k_1)) + r(p(k_1 + i)) = N - (N-\#\text{boxes in first }p(k_1)\text{ cols} + \cdots)\ne $~\Cref{eq:rcols}. We want to apply $p$ to $\{1,\dots,i\}$ and not just $i$. I guess we could clarify/declare that $r(p(i)) = N - \#$ boxes in columns $p(1),\dots,p(i)$. For a minute I thought it was actually fine, but what we have is: $r_{z(s),j}(i) = N - (\#\text{boxes in cols }1,\dots,p(k_j + i) - \#\text{boxes in cols }1,\dots,p(k_j))$ and what we want is $\dots (\#\text{boxes in cols }p(1),\dots,p(k_j + i) - \#\text{boxes in cols }p(1),\dots,p(k_j + i))$ right?}
% 
%\jcom{I fixed the definition of $ r_{z,j}(i)$, so now it is correct, I believe.  I changed the wording of ``reproduce''. I'm trying to say that $ p$ is used to define $ z(s)$ and the we get $ p $ back from $ z(s)$ as the permutation coming from the equalities.}
%\acom{\emoji{+1}}
% 
Let $ W = \{ z(s) : s \in \CC \}$. Combining \Cref{eq:ranks,eq:ESfibre,eq:rcols,eq:rcol2},
% (\ref{eq:ranks}), (\ref{eq:ESfibre}), (\ref{eq:rcols}), (\ref{eq:rcols2}) 
we see that the Eisenbud--Saltman family $ X_{r, W} \rightarrow W $ gives our family $ \overline{\OO}^{\lambda', \lambda''}_{0, \AA}$.
\end{proof}
% 
% 
% The family of adjoint orbits $  whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ and whose \acom{Claim:} fibre over 0 is $\overline{\OO}^\lambda$ (a consequence of Eisenbud and Salten's characterization of ``rank varieties'' as proved in \Cref{cor:es}). \acom{TODO: make into definition to be x-referenced in proof of description of fibres}
% 
% \jcom{We should justify why the 0 fibre is correct scheme-theoretically.} 
%\acom{does it follow because ``$s$ divides $\det g$'' is a closed condition 
%in $\AA_s\times \AA_{\det}$? 
%so the set of $A$ which are conjugate to
%$J_{0,\lambda'} \oplus J_{s,\lambda''}$
%by a matrix whose determinant is divisible by $s$ is also closed?}
%\jcom{I didn't follow your argument. One approach would be to write down the generators for the ideal of $\overline{\OO}^{\lambda', \lambda''}_{0,s} $ and then set $ s =0$.  For example, take $ \lambda' = (1) = \lambda'' $ (I know it is a small example!), then the ideal is generated by $ tr(A) = s$, $det(A) = 0$, so when we take $ s =0$, we get just $ tr(A) = 0, det(A) = 0$.  I am hoping that we can find a reference for this result somewhere.}
%\acom{I thought that the point would be to show that a dense subset of matrices which are conjugate to $J_{0,\lambda'}\oplus J_{s,\lambda''}$ limit to matrices which are conjugate to $J_\lambda$. In particular, that the conjugating matrix remains invertible in the $s\to0$ limit.}
% 
% TODO: delete commented out remark and subcomment!
% \begin{remark}
\begin{comment}
Base case $m = 1$: by a slight abuse of notation let $\lambda', \lambda_2 \in \NN$. Claim: $J=J_{0,\lambda'} \oplus J_{s,\lambda_2}$ is conjugate to

@@

The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is defined to be the affine space of matrices of the form

@@

$J_{0,\mu} + x$ where $x$ is a $\mu\times\mu$ block matrix with possibly nonzero entries in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 

@@

By example, if 
% $\mu=(3,2,2,1)$, 
$\mu = (3,2)$ then $A\in\TT_\mu$ looks like 
\[
    \left[
        \begin{BMAT}(e){ccc;cc}{ccc;cc} 
        0 & 1 & 0 & 0 & 0\\
        0 & 0 & 1 & 0 & 0\\
        A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
        0 & 0 & 0 & 0 & 1\\
        A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
        \end{BMAT}\right] 
    % TODO: REDO 
    % \left[
    %     \begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
    %         & 1 & & & & & \\
    %         &  & 1 & & & & \\
    %     A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
    %         &  & &  & 1 & & \\
    %         A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
    %         A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
    %         A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
    % \end{BMAT}
    % \right] % \,. 
\]
for some $A_{ij}^k\in\CC$. 
% \[
%     \left[\begin{BMAT}(e){c;cc;cc;ccc}{c;cc;cc;ccc} 
%         0 & A_0 & A_1 & A_2 & A_3 & A_4 & A_5 & A_6\\
%         0 & 0 & 1 & 0 & 0 & 0 & 0 & 0\\
%         0 & 0 & 0 & A_7 & A_8 & A_9 & A_{10} & A_{11}\\
%         0 & 0 & 0 & 0 & 1 & 0 & 0 & 0\\
%         0 & 0 & 0 & 0 & 0 & A_{12} & A_{13} & A_{14}\\
%         0 & 0 & 0 & 0 & 0 & 0 & 1 & 0\\
%         0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
%         0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
%         \end{BMAT}\right]
% \]
%

To $ A \in \TT_\mu$ we will associate the $m\times m$ matrix 
of polynomials 
% $ g(A) = \left( g(A)_{ij} \right)$ 
$g(A)$ in $ M_m(\CC[t]) $ whose $(i,j)$th entry is defined as follows.
\begin{equation}
    \label{eq:mvyofa}
    g(A)_{ij} = 
\begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j\,, \\
    % A^k_{ji} t^{k-1} & i = j \\
        % \text{ if $ i = j$} \\
        - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j\,. 
    %  \text{ if $ i \ne j$ }
\end{cases}
\end{equation}
$A^k_{ji}$ denotes the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
%

@@

In other words, the $ i,j$ block of $ A $ is used to produce a polynomial which is inserted in the $ j,i$ entry of $ g(A)$.

@@

We record the following easy observations.
\begin{lemma} \label{le:rdimTrans} Let $ L \in \Gr_+$.
\begin{enumerate}
    \item For any $ 
    \gamma \subset [m] $, we have $$ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L \,.$$
    \item For any $ \gamma_1 \subset \gamma_2 \subset [m]$, we have $$ (L_{\gamma_2})_{\gamma_1} = L_{\gamma_1}
$$
\end{enumerate}
\end{lemma}
\acom{Doesn't the identification $G(K)/G(O) \to G(O)\ G(K)$ coming from $g\mapsto g^{-1}$ give us a minus sign somewhere, since we are sending $S^\mu_w$ to $S^{-\mu}_w$, so $D_{\omega_i}(L) = -\rdim L_{[1,i]}$. Ignoring the minus sign for now, for $j\le i\le m$, and $L_{[1,i]}$ in $S^{\mu(i)}_- \cap S^{\lambda(i)}_+$ we’d like $D_{\omega_j}(L_{[1,i]}) = \rdim (L_{[1,i]})_{[1,j]} = \lambda(i)_j + \cdots + \lambda(i)_i$ whereas the claim $(L_{[1,i]})_{[1,j]} = L_{[1,j]}$ hides that this lattice also depends on $i$? I'm sure I'm missing something here so I will look at it again later. $n_{(a,b)} (L_{[1,i]}) = -D_{[a+1,b]} - D_{[a , b-1]} + D_{[a + 1, b-1]} + D_{[a,b]} = - \rdim L_{[a+1,b]} - \rdim L_{[a,b-1]} + \rdim L_{[a+1,b-1]} + \rdim L_{[a,b]}$}
\jcom{I warned you when we talked on Tuesday that there might be some problems, but I think that we shouldn't dig any deeper here.} 
\acom{Well, it's not that deep.. it's just that $(L_{\gamma_1})_{\gamma_2}$ involves taking $\gamma_2^c\subset \gamma_1$ and landing in $\cO^{\gamma_1\cap\gamma_2}$ whereas $L_{\gamma_2}$ involves taking $\gamma_2^c\subset[m]$ and landing in $\cO^{\gamma_2}$ ...so I think the change makes it true.}
\jcom{But I assumed that $ \gamma_1 \subset \gamma_2$, so I don' think that taking intersection is necessary.}
\acom{Even so? What was written before was $(L_{\gamma_1})_{\gamma_2} = L_{\gamma_2} $ and if $\gamma_1\subset\gamma_2$ then the intersection is $\gamma_1$. Anyway I don't think we ever use Lem. 6(2), so we can do without it?}
\jcom{Oh, I guess there was a typo.  I fixed it now.  It is used in the proof of Prop 4, I will add a reference.}

@@

For this section only, we will write $ S^\mu_- = N_-(\cK) t^\mu$ (previously we left out the subscript). We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
% \acom{Maybe we shouldn't decorate $S^\mu$ with a subscript $-$ after all since we certainly won't want to add to $S^{\mu',\mu''}_{0,\AA}$ in underscores.}
% \jcom{I agree.  Is the above solution ok?}
% \acom{Sure.}
% 
% \jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
% \acom{For it.}
% \acom{As was checked in \cite{dranowski2020generalized} $S^\mu_w = \{D_{w\omega_i} = \langle \mu , w w_0 \omega_i\rangle \}$ so $S^\mu_+ = \{D_{\omega_i}(L) = \rdim L^{w_0\omega_i} \}$} 
% \jcom{But that was for a different identification of the left and right quotients.  I'm certain that the statements in the Lemma below are correct.}

@@

The equivalence of \ref{Srdim2} and \ref{Srdim3} follows from Lemma \ref{le:rdimTrans}.
\end{proof}
\jcom{I added a proof.  We can get delete and just put a reference to mvcycle if you prefer.}

\acom{No no this is good! Thanks for other additions}

>>>>

\subsection{The fusion construction}
\label{ss:fuscon}
\jcom{We should probably be consistent with $ \AA$ vs $\CC$.  I'm happy with either.}
\acom{Do you mean that if we go with $\AA$ we should change $\AA^\times$ as well? Also, would you agree that the distinction is the topology? So $\AA$ is better if we were using ``generic'' to describe $s\ne 0$, which we are not.}
\jcom{Yes, either we should write $ \AA, \AA^\times $ or $ \CC, \AA^\times$.  There is no distinction.  Always in this paper, we work with the Zariski topology whether we write $ \AA $ or $ \CC$.}
\acom{Ok, let's be fancy and write $\AA$. (So if someone writes $s\to 0$ you don't think of it as $s$ approaches $0$ in the metric topology, but really as the limit of ideals $(s)\supset (s^2)\supset \cdots$ which, I hope, is the zero ideal?)}

@@

Given $ s \in \AA$ we write $ J_{s,\lambda}$ for the Jordan form matrix with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$.

\begin{definition}
\label{def:Olam}
The nilpotent (adjoint) orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$. These matrices and the linear operators they represent will be said to have Jordan type $\lambda$.
\end{definition}  
% 
% Temporarily commenting out, don't use
% Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
% 
\begin{definition}
\label{def:Olamlam}
    For $ s \in \CC, s \ne 0$, the (adjoint) orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
    These matrices and the linear operators they represent will be said to have Jordan type $((0,\lambda'), (s,\lambda''))$.
\end{definition}  
%

@@

We recall that these orbits have closures which are given by rank conditions.  
More precisely, we have
$$
    \overline{\OO}^\lambda = \{ A \in M_N(\CC) : \rk A^i \le N - \#\text{~boxes in first $i$ columns of }\lambda \}
$$
and
\begin{equation} 
\label{eq:ranks}
\begin{split}
    % 
    \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : \rk A^i &\le N - 
    \#\text{~boxes in first $i$ columns of }\lambda' \\
    \rk (A-s)^i &\le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}\,. 
\end{split}
\end{equation}
%

@@

Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ called a \new{rank function}.  Let $k $ be maximal such that $ r(k) \ne 0 $.
% \jcom{I don't know if it is really necessary to introduce this $ k$.  Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.} \acom{And make it $N$? Was $k = m$ replaced because $m$ is already used?} \jcom{Yes and yes} \acom{I like the idea of making it $N$}
% 
Let $ W$ be a subspace of $ \AA^k$. Eisenbud and Saltman define and study the flat family $ X_{r,W} \rightarrow W$, whose fibres are reduced and defined by rank conditions. We will now describe these fibres.

Let $ z \in \AA^k$. Some of the coordinates of $z$ may be equal; we introduce some data to keep track of these equalities. There exist a sequence of integers $k_\bullet = (k_0,\dots,k_\ell)$ such that $ 0=k_0< k_1< \dots < k_\ell = k $, a sequence of points $s_\bullet = (s_1, \dots, s_\ell )\in\AA^\ell$ such that $s_i\ne s_j$ for any $i\ne j$, and a permutation  $ p $ of $ \{1, \dots, k\}$ such that 
$$ s_j = z_{p(k_{j-1}+1)} = z_{p(k_{j-1} + 2)} =  \cdots = z_{p(k_j)}$$ 
for each $j = 1,\dots,\ell$. 
Given the choice of $ s_\bullet$ we require that $ p $ is of minimal length. 
Given $z$, the data $k_\bullet, s_\bullet, p$ is unique up to a permutation of $ \{1, \dots, \ell\}$.
% 
%\jcom{Eisenbud--Saltman don't introduce this $ s_j$ notation, but I find it helpful.}
% 
%\acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}
%\jcom{That is what I was trying to say with ``introduce some data \dots''  Maybe it could be more clear.  I also clarified the uniqueness.}
%\acom{Oh, sorry, I see it. Maybe because it was the start of a new paragraph I didn't connect `data' and `ranks' at first glance.}

Next for $ j = 1, \dots \ell $ and $ i = 1, \dots, k_{j+1} - k_j$, we define
$$
    % r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
    r_{z,j}(i):= N + \sum_{a = 1}^i r(p(k_j + a)) - r(p(k_j +a) - 1)  \, . 
$$
\jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
\acom{I don't think that there is any need to swap back. But maybe we could use $c$ (for column) isntead of $i$, since we use $i$ in the same context quite a bit to denote a letter in the alphabet $\{1,\dots,m\}$.} 
%\jcom{I fixed it now.  I didn't want to use ES's $a_i$.} 
%\acom{\emoji{+1}}

@@

For $ s \in \AA$, we define $ z(s) \in \AA^k$ by 
\[
\begin{cases}
    z(s)_{p(j)} = 0 &  j = 1, \dots, k_1 \\
    z(s)_{p(j)} = s & j = k_1 + 1, \dots, k\,.
\end{cases}    
\]
% $ z(s)_{p(j)} = 0 $ for $ j = 1, \dots, k_1 $ and $ z(s)_{p(j)} = s $ for $ j = k_1 + 1, \dots, k$.

For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of 
\(\ell =2\), \(k_\bullet = (0,\lambda_1')\), \(s_\bullet = (0,s)\) and the permutation $p$.
% $ \ell = 2$, $k_1$, $s_1 = 0$, $s_2 = s$, and the permutation $p $.
We also see that
\begin{equation} 
\label{eq:rcols}
    \begin{split}
            r_{z(s), 1}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda' \\
            r_{z(s), 2}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda'' \,. 
    \end{split}
\end{equation}
On the other hand, for $z(0)$, we get that $ \ell = 1$ and that \acom{This was $r = 1$ but I think it should be $\ell = 1$.}
\begin{equation} 
\label{eq:rcol2}
    r_{z(0),1}(i) = 
    r(i) = N - \#\text{~boxes in first $i$ columns of }\lambda\,. 
\end{equation}
%\jcom{Someone should check that I chose the notation correctly to make this work out.}
% 
%\acom{What do we mean by equalities in $z(s)$ reproduce $p$? I thought $z(s)$ was defined by $p$. Also, $r_{z(s),1}(i) = N- r(p(k_1)) + r(p(k_1 + i)) = N - (N-\#\text{boxes in first }p(k_1)\text{ cols} + \cdots)\ne $~\Cref{eq:rcols}. We want to apply $p$ to $\{1,\dots,i\}$ and not just $i$. I guess we could clarify/declare that $r(p(i)) = N - \#$ boxes in columns $p(1),\dots,p(i)$. For a minute I thought it was actually fine, but what we have is: $r_{z(s),j}(i) = N - (\#\text{boxes in cols }1,\dots,p(k_j + i) - \#\text{boxes in cols }1,\dots,p(k_j))$ and what we want is $\dots (\#\text{boxes in cols }p(1),\dots,p(k_j + i) - \#\text{boxes in cols }p(1),\dots,p(k_j + i))$ right?}
% 
%\jcom{I fixed the definition of $ r_{z,j}(i)$, so now it is correct, I believe.  I changed the wording of ``reproduce''. I'm trying to say that $ p$ is used to define $ z(s)$ and the we get $ p $ back from $ z(s)$ as the permutation coming from the equalities.}
%\acom{\emoji{+1}}
% 
Let $ W = \{ z(s) : s \in \CC \}$. Combining \Cref{eq:ranks,eq:ESfibre,eq:rcols,eq:rcol2},
% (\ref{eq:ranks}), (\ref{eq:ESfibre}), (\ref{eq:rcols}), (\ref{eq:rcols2}) 
we see that the Eisenbud--Saltman family $ X_{r, W} \rightarrow W $ gives our family $ \overline{\OO}^{\lambda', \lambda''}_{0, \AA}$.
\end{proof}
% 
% 
% The family of adjoint orbits $  whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ and whose \acom{Claim:} fibre over 0 is $\overline{\OO}^\lambda$ (a consequence of Eisenbud and Salten's characterization of ``rank varieties'' as proved in \Cref{cor:es}). \acom{TODO: make into definition to be x-referenced in proof of description of fibres}
% 
% \jcom{We should justify why the 0 fibre is correct scheme-theoretically.} 
%\acom{does it follow because ``$s$ divides $\det g$'' is a closed condition 
%in $\AA_s\times \AA_{\det}$? 
%so the set of $A$ which are conjugate to
%$J_{0,\lambda'} \oplus J_{s,\lambda''}$
%by a matrix whose determinant is divisible by $s$ is also closed?}
%\jcom{I didn't follow your argument. One approach would be to write down the generators for the ideal of $\overline{\OO}^{\lambda', \lambda''}_{0,s} $ and then set $ s =0$.  For example, take $ \lambda' = (1) = \lambda'' $ (I know it is a small example!), then the ideal is generated by $ tr(A) = s$, $det(A) = 0$, so when we take $ s =0$, we get just $ tr(A) = 0, det(A) = 0$.  I am hoping that we can find a reference for this result somewhere.}
%\acom{I thought that the point would be to show that a dense subset of matrices which are conjugate to $J_{0,\lambda'}\oplus J_{s,\lambda''}$ limit to matrices which are conjugate to $J_\lambda$. In particular, that the conjugating matrix remains invertible in the $s\to0$ limit.}
% 
% TODO: delete commented out remark and subcomment!
% \begin{remark}
\begin{comment}
Base case $m = 1$: by a slight abuse of notation let $\lambda', \lambda_2 \in \NN$. Claim: $J=J_{0,\lambda'} \oplus J_{s,\lambda_2}$ is conjugate to

@@

Recall that $\mu=(\mu_1,\dots,\mu_m)$ is a partition of $N$. The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is the affine space of $N\times N$ matrices of the form

@@

$J_{0,\mu} + x$ where $x$ is a $\mu\times\mu$ block matrix with possibly nonzero entries $A_{ij}^1,\dots,A_{ij}^{\min(\mu_i,\mu_j)}$ in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 

@@

By example, if 
% $\mu=(3,2,2,1)$, 
$\mu = (3,2)$ then $A\in\TT_\mu$ looks like 
\[
    \left[
        \begin{BMAT}(e){ccc;cc}{ccc;cc} 
        0 & 1 & 0 & 0 & 0\\
        0 & 0 & 1 & 0 & 0\\
        A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
        0 & 0 & 0 & 0 & 1\\
        A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
        \end{BMAT}\right] 
    % TODO: REDO 
    % \left[
    %     \begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
    %         & 1 & & & & & \\
    %         &  & 1 & & & & \\
    %     A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
    %         &  & &  & 1 & & \\
    %         A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
    %         A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
    %         A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
    % \end{BMAT}
    % \right] % \,. 
\]
for some $A_{ij}^k\in\AA$. 
% \[
%     \left[\begin{BMAT}(e){c;cc;cc;ccc}{c;cc;cc;ccc} 
%         0 & A_0 & A_1 & A_2 & A_3 & A_4 & A_5 & A_6\\
%         0 & 0 & 1 & 0 & 0 & 0 & 0 & 0\\
%         0 & 0 & 0 & A_7 & A_8 & A_9 & A_{10} & A_{11}\\
%         0 & 0 & 0 & 0 & 1 & 0 & 0 & 0\\
%         0 & 0 & 0 & 0 & 0 & A_{12} & A_{13} & A_{14}\\
%         0 & 0 & 0 & 0 & 0 & 0 & 1 & 0\\
%         0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
%         0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
%         \end{BMAT}\right]
% \]
%

To $ A \in \TT_\mu$ we will associate the $m\times m$ matrix of polynomials 
% $ g(A) = \left( g(A)_{ij} \right)$ 
$g(A)$ in $ M_m(\AA[t]) $ whose $(i,j)$th entry is defined as follows.
\begin{equation}
    \label{eq:mvyofa}
    g(A)_{ij} = 
\begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j\,, \\
    % A^k_{ji} t^{k-1} & i = j \\
        % \text{ if $ i = j$} \\
        - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j\,. 
    %  \text{ if $ i \ne j$ }
\end{cases}
\end{equation}
% $A^k_{ji}$ denotes the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
%

@@

In other words, the $ \mu_i\times\mu_j$ block of $ A $ is used to produce a polynomial which is inserted in the $(j,i)$ entry of $ g(A)$.

@@

We record the following easy observations.
\begin{lemma} \label{le:rdimTrans} Let $ L \in \Gr_+$.
\begin{enumerate}
    \item For any $ 
    \gamma \subset [m] $, we have $$ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L \,.$$
    \item For any $ \gamma_1 \subset \gamma_2 \subset [m]$, we have $$ (L_{\gamma_2})_{\gamma_1} = L_{\gamma_1}
$$
\end{enumerate}
\end{lemma}
% \acom{Doesn't the identification $G(K)/G(O) \to G(O)\ G(K)$ coming from $g\mapsto g^{-1}$ give us a minus sign somewhere, since we are sending $S^\mu_w$ to $S^{-\mu}_w$, so $D_{\omega_i}(L) = -\rdim L_{[1,i]}$. Ignoring the minus sign for now, for $j\le i\le m$, and $L_{[1,i]}$ in $S^{\mu(i)}_- \cap S^{\lambda(i)}_+$ we’d like $D_{\omega_j}(L_{[1,i]}) = \rdim (L_{[1,i]})_{[1,j]} = \lambda(i)_j + \cdots + \lambda(i)_i$ whereas the claim $(L_{[1,i]})_{[1,j]} = L_{[1,j]}$ hides that this lattice also depends on $i$? I'm sure I'm missing something here so I will look at it again later. $n_{(a,b)} (L_{[1,i]}) = -D_{[a+1,b]} - D_{[a , b-1]} + D_{[a + 1, b-1]} + D_{[a,b]} = - \rdim L_{[a+1,b]} - \rdim L_{[a,b-1]} + \rdim L_{[a+1,b-1]} + \rdim L_{[a,b]}$}
% \jcom{I warned you when we talked on Tuesday that there might be some problems, but I think that we shouldn't dig any deeper here.} 
% \acom{Well, it's not that deep.. it's just that $(L_{\gamma_1})_{\gamma_2}$ involves taking $\gamma_2^c\subset \gamma_1$ and landing in $\cO^{\gamma_1\cap\gamma_2}$ whereas $L_{\gamma_2}$ involves taking $\gamma_2^c\subset[m]$ and landing in $\cO^{\gamma_2}$ ...so I think the change makes it true.}
% \jcom{But I assumed that $ \gamma_1 \subset \gamma_2$, so I don' think that taking intersection is necessary.}
% \acom{Even so? What was written before was $(L_{\gamma_1})_{\gamma_2} = L_{\gamma_2} $ and if $\gamma_1\subset\gamma_2$ then the intersection is $\gamma_1$. Anyway I don't think we ever use Lem. 6(2), so we can do without it?}
% \jcom{Oh, I guess there was a typo.  I fixed it now.  It is used in the proof of Prop 4, I will add a reference.}

@@

In this section only, we will write $ S^\mu_- = N_-(\cK) t^\mu$ (previously we left out the subscript). We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$. \acom{HB, ``..we will write.., because we will need the opposite cell..''}
% \acom{Maybe we shouldn't decorate $S^\mu$ with a subscript $-$ after all since we certainly won't want to add to $S^{\mu',\mu''}_{0,\AA}$ in underscores.}
% \jcom{I agree.  Is the above solution ok?}
% \acom{Sure.}
% 
% \jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
% \acom{For it.}
% \acom{As was checked in \cite{dranowski2020generalized} $S^\mu_w = \{D_{w\omega_i} = \langle \mu , w w_0 \omega_i\rangle \}$ so $S^\mu_+ = \{D_{\omega_i}(L) = \rdim L^{w_0\omega_i} \}$} 
% \jcom{But that was for a different identification of the left and right quotients.  I'm certain that the statements in the Lemma below are correct.}

@@

The equivalence of \ref{Srdim2} and \ref{Srdim3} follows from Lemma \ref{le:rdimTrans}.
\end{proof}
% \jcom{I added a proof.  We can get delete and just put a reference to mvcycle if you prefer.}

% \acom{No no this is good! Thanks for other additions}
